Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-05-29 sec_results.tex
adding fig5
adding Fig2
adding new figure

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively. }

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_RidgeYield_Esel_py.pdf}
	\caption{The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
	\label{fig:RidgeYield_ESE}
\end{figure}

@@

\section{Model Comparison}
\label{sec:theory}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively. }
	\label{fig:PlotDeltaPhi}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
	\label{fig:RidgeYield_ESE}
\end{figure}

@@
